---
title: "M01-2-Introduction to Literate Programming-Application Assignment"
author: "Luyao Liu"
date: '`r format(Sys.time())`'
format: 
  html: 
    toc: true
    toc-depth: 4
    number-sections: true
    code-line-numbers: true
    code-fold: false
    code-link: true
    embed-resources: true
editor: visual
execute: 
  freeze: auto
  warning: false
---

```{R}
library(ggplot2)
library(dplyr)
```

# Create a variable called X and assign the text

### ***Creat variable X***

```{r}
X <- "This is my first assignment"
```

# Text Manipulation

## Explore paste()

### *Understanding string concatenation*:

```{r}
paste("Hello", "World", sep = "_")
paste0("Case", 1:3)                   
```

## Updating X

### *String concatenation*:

```{r}
X_updated <- paste(X, "and I'm loving it!")
```

# Vector Operations

```{r}
Y <- c(2, 3, 4, 5) * 2  
```

# Print variables X and Y

```{r}
X
Y
```

# Max and min of vector Y

```{r}
max(Y)
min(Y)
```

# Load ggplot2 and view economics data

```{r}
library(ggplot2)
head(economics)
```

# Economics data visualization

```{r}
plot <- ggplot(economics, aes(x = unemploy, y = uempmed)) +
  geom_point() +
  labs(title = "Unemployment vs. Median Unemployment Duration",
       x = "Number of Unemployed (thousands)",
       y = "Median Duration (weeks)")
plot
```

# Enhanced Visualization

::: {.callout-important}\
#\| icon: false\
**Must load dependencies for pipe operator!**\
:::

```{r}
#| label: fig-unemployment
#| fig-cap: "Unemployment trends (cross-reference @fig-unemployment)"
#| fig-width: 5
#| fig-aspect-ratio: 0.6

library(dplyr)   # Essential for pipe
library(ggplot2) # Visualization

economics %>%
  ggplot(aes(x = unemploy/1000, y = uempmed)) +  # Proper scaling
  geom_point(alpha = 0.6, color = "navyblue") +
  labs(
    title = "Unemployment Analysis",
    x = "Unemployed (Thousands)",
    y = "Median Duration (Weeks)",
    caption = "Source: ggplot2 Economics Dataset"
  )
```

# Key Findings

::: callout-note
#\| icon: false As shown in @fig-unemployment, there's a clear positive correlation between unemployment numbers and duration. This suggests: - Labor market saturation during high unemployment - Potential skills mismatch in economic downturns - Need for policy interventions during prolonged unemployment
:::

# Formatting Summary

1.  **Hierarchical Headings**: Used `#`, `##`, `###` for document structure\
2.  **Text Emphasis**:
    -   **Bold** for variable definitions\
    -   *Italics* for conceptual explanations\
3.  **Callouts**:
    -   `callout-tip` for best practices\
    -   `callout-note` for observations\
    -   `callout-important` for critical reminders\
4.  **Code Integration**:
    -   `blockquote` formatting for code context\
    -   Backticks (`) for function references like`paste()\`\
5.  **Cross-referencing**: Implemented via `@fig-label` system\
6.  **Chunk Control**: Used `#|` options for figure sizing and labels\
7.  **List Structures**: Bullet points for findings and numbered lists for summaries\
8.  **Visual Consistency**: Color-coded geoms and proper axis scaling\
9.  **Dependency Management**: Explicit package loading within chunks\
10. **Semantic Markers**: Font Awesome icons for visual cues :::
