---
title: "M01-2-Introduction to Literate Programming-Application Assignment"
author: "Luyao Liu"
date: '`r format(Sys.time())`'
format: 
  html: 
    toc: true
    toc-depth: 4
    number-sections: true
    code-line-numbers: true
    code-fold: false
    code-link: true
    embed-resources: true
editor: visual
execute: 
  freeze: auto
  warning: false
---
```{R}
library(ggplot2)
library(dplyr)
```

# 1. Create a variable called X and assign the text

**Creat variable X**
```{r}
# Assigning text to variable X
X <- "This is my first assignment"
```

# 2. Text Manipulation

## 2.1 Explore paste()

* Examples base R string functions*:
```{r}
# paste() vs paste0() comparison
paste("Hello", "World", sep = "_")    # Output: "Hello_World"
paste0("Case", 1:3)                   # Output: "Case1" "Case2" "Case3"
```

## 2.2 Updating X 
```{r}
X_updated <- paste(X, "and I'm loving it!")
```

# 3. Vector Operations 
```{r}
Y <- c(2, 3, 4, 5) * 2  # Direct element-wise multiplication
```


# 4. Print variables X and Y
```{r}
# Display values of X and Y
X
Y
```

# 5. Max and min of vector Y
```{r}
# Calculate maximum and minimum values
max(Y)
min(Y)
```

# 6. Load ggplot2 and view economics data
```{r}
library(ggplot2)
head(economics)
```

# 7. Economics data visualization
```{r}
# Create scatter plot of unemployment vs. median unemployment duration
plot <- ggplot(economics, aes(x = unemploy, y = uempmed)) +
  geom_point() +
  labs(title = "Unemployment vs. Median Unemployment Duration",
       x = "Number of Unemployed (thousands)",
       y = "Median Duration (weeks)")
plot
```

# 8. Enhanced Visualization 

```{r}
#| label: fig-unemployment
#| fig-cap: "Unemployment trends (cross-reference @fig-unemployment)"
#| fig-width: 5
#| fig-aspect-ratio: 0.6

library(dplyr)   # Essential for pipe
library(ggplot2) # Visualization

economics %>%
  ggplot(aes(x = unemploy/1000, y = uempmed)) +  # Proper scaling
  geom_point(alpha = 0.6, color = "navyblue") +
  labs(
    title = "Unemployment Analysis",
    x = "Unemployed (Thousands)",
    y = "Median Duration (Weeks)",
    caption = "Source: ggplot2 Economics Dataset"
  )
```

# 9. Key Findings 

::: {.callout-note}
#| icon: false
As shown in @fig-unemployment, there's a clear positive correlation between unemployment numbers and duration. This suggests:
- Labor market saturation during high unemployment
- Potential skills mismatch in economic downturns
- Need for policy interventions during prolonged unemployment
:::

# 10. Formatting Summary 

1. **Hierarchical Headings**: Used `#`, `##`, `###` for document structure  
2. **Text Emphasis**:  
   - **Bold** for variable definitions  
   - *Italics* for conceptual explanations  
3. **Callouts**:  
   - `callout-tip` for best practices  
   - `callout-note` for observations  
   - `callout-important` for critical reminders  
4. **Code Integration**:  
   - `blockquote` formatting for code context  
   - Backticks (`) for function references like `paste()`  
5. **Cross-referencing**: Implemented via `@fig-label` system  
6. **Chunk Control**: Used `#|` options for figure sizing and labels  
7. **List Structures**: Bullet points for findings and numbered lists for summaries  
8. **Visual Consistency**: Color-coded geoms and proper axis scaling  
9. **Dependency Management**: Explicit package loading within chunks  
10. **Semantic Markers**: Font Awesome icons for visual cues
:::


